NGO Crackdowns and Philanthropy

### 2019-03-08 analysis/01_clean-data.Rmd
HUGE reorganization (go to 0290370 for previous history)
Switched this to build as a package using rrtools, with pre-built Stan binaries through rstantools. As a result, everything got shuffled around, and GitHub doesn't use --follow in their logs, so the history is hidden. Going to 02903709c87b79e8a945dd31fafd2484cbf2bc7b and going back in history from there will let you see past changes to these files.

In general, here's what happened:

- All analysis files in the project root (Rmd files that generated the website) are now in /analysis/*
- R functions that lived in lib/* are now standalone

```{r clean-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(here)
library(csvy)

# Calculate the quantile (and median) of an ordered factor
# Borrowed from @jrnold: https://gist.github.com/jrnold/6759254
#
# In the case of ties, the first in order will win. For instance, 
# bloop <- factor(c("A", "A", "B", "B"), ordered = TRUE)
# median(bloop)  # "A"
quantile.ordered <- function(x, probs = seq(0, 1, 0.25)) {
  tab <- table(x)
  cdf <- cumsum(tab / sum(tab))
  idx <- sapply(probs, function(p) min(which(cdf >= p)))
  levels(x)[idx] 
}

quantile.factor <- quantile.ordered
median.ordered <- function(x) quantile(x, 0.5)
median.factor <- median.ordered

# Load data
# results_file <- file.path(here(), "data", "test_data.csv")
results_file <- here("private", 
                     "NGO Crackdowns and Philanthropy, March 2018 pilot_March 23, 2018_20.01.csv")

@@

# Confirmation codes to exclude. These are people who failed the attention
# checks or who took the survey outside of MTurk.
#
# The code for determining these is in a script that is excluded from the main
# repository because of privacy issues (it deals directly with MTurk worker
# IDs), called "private/approve_mturkers.R". It outputs this text list of codes.
codes_to_exclude <- read_csv(here("data", "codes_to_exclude.csv"))

@@

# Save final clean data
saveRDS(results, here("data", "results_clean.rds"))
write_csvy(results, file = here("data", "results_clean.csv"),
           metadata = here("data", "results_clean.yaml"), na = "NA")
```

@@

saveRDS(completed_summary, here("data", "completion_summary.rds"))
write_csv(completed_summary, here("data", "completion_summary.csv"))
```

>>>>

```{r clean-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(crackdownsphilanthropy)
library(csvy)
library(here)

# Load data
# results_file <- file.path(here(), "data", "test_data.csv")
results_file <- here("data", "private_data", 
                     "NGO Crackdowns and Philanthropy, March 2018 pilot_March 23, 2018_20.01.csv")

@@

# Confirmation codes to exclude. These are people who failed the attention
# checks or who took the survey outside of MTurk.
#
# The code for determining these is in a script that is excluded from the main
# repository because of privacy issues (it deals directly with MTurk worker
# IDs), called "data/private_data/approve_mturkers.R". It outputs this text list
# of codes.
codes_to_exclude <- read_csv(here("data", "derived_data", "codes_to_exclude.csv"))

@@

# Save final clean data
saveRDS(results, here("data", "derived_data", "results_clean.rds"))
write_csvy(results, file = here("data", "derived_data", "results_clean.csv"),
           metadata = here("data", "derived_data", "results_clean.yaml"), na = "NA")
```

@@

saveRDS(completed_summary, here("data", "derived_data", "completion_summary.rds"))
write_csv(completed_summary, here("data", "derived_data", "completion_summary.csv"))
```

### 2019-03-08 analysis/02_analysis.Rmd
HUGE reorganization (go to 0290370 for previous history)
Switched this to build as a package using rrtools, with pre-built Stan binaries through rstantools. As a result, everything got shuffled around, and GitHub doesn't use --follow in their logs, so the history is hidden. Going to 02903709c87b79e8a945dd31fafd2484cbf2bc7b and going back in history from there will let you see past changes to these files.

In general, here's what happened:

- All analysis files in the project root (Rmd files that generated the website) are now in /analysis/*
- R functions that lived in lib/* are now standalone

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(rstan)
library(tidybayes)
library(broom)
library(ggstance)
library(ggdag)
library(patchwork)
library(pander)
library(scales)
library(janitor)
library(huxtable)
library(here)

source(here("lib", "graphics.R"))
source(here("lib", "pander_options.R"))
source(here("lib", "modeling.R"))

# Load data
results <- readRDS(here("data", "results_clean.rds"))
# qwraps2::lazyload_cache_dir("02_analysis_cache/html")

# Helpful functions
safe_mean <- function(x, ...) suppressWarnings(mean(as.numeric(x), ...))
safe_sd <- function(x, ...) suppressWarnings(sd(as.numeric(x), ...))

my_as_numeric <- function(x) {
  is_num <- suppressWarnings(!any(is.na(as.numeric(x))))

  if (is_num) {
    as.numeric(x)
  } else {
    x
  }
}

level_summary <- function(x, variable, df = results) {
  variable <- as.character(variable)
  if (is.factor(df[[variable]])) {
    x_levels <- levels(df[[variable]])
  } else {
    x_levels <- unique(df[[variable]])
  }

  factor_summary <- tibble(x) %>% 
    count(x) %>%
    mutate(pct = n / sum(n),
           fancy = paste0(x, " (", n, "; ", percent(pct), ")"),
           x = factor(x, levels = x_levels, ordered = TRUE))

  inline_summary <- factor_summary %>% arrange(x) %>% 
    pull(fancy) %>% paste(collapse = " | ")

  fig_bar <- ggplot(factor_summary, aes(x = x, y = n)) +
    geom_bar(stat = "identity", fill = "grey50") +
    theme_spark()

  file_name <- gsub("\\.| ", "_", tolower(variable))
  md_img <- paste0("![](output/figures/summary-table/", file_name, ")")

  ggsave(fig_bar, filename = here("output", "figures", "summary-table",
                                  paste0(file_name, ".pdf")), 
         width = 1, height = 0.2, device = cairo_pdf)
  ggsave(fig_bar, filename = here("output", "figures", "summary-table",
                                  paste0(file_name, ".png")), 
         width = 1, height = 0.2, type = "cairo", bg = "transparent", dpi = 300)

  output <- tibble(spark = md_img, summary = inline_summary)
  return(output)
}

numeric_summary <- function(x, variable) {
  inline_summary <- paste0("Median: ", round(median(x, na.rm = TRUE), 2),
                           " | Mean: ", round(mean(x, na.rm = TRUE), 2), 
                           " | Std. Dev.: ", round(sd(x, na.rm = TRUE), 2))

  fig_hist <- ggplot(as.data.frame(x), aes(x = x)) +
    geom_histogram(fill = "grey50", binwidth = 10) +
    theme_spark()

  file_name <- gsub("\\.| ", "_", tolower(variable))
  md_img <- paste0("![](output/figures/summary-table/", file_name, ")")

  ggsave(fig_hist, filename = here("output", "figures", "summary-table",
                                   paste0(file_name, ".pdf")), 
         width = 1, height = 0.2, device = cairo_pdf)
  ggsave(fig_hist, filename = here("output", "figures", "summary-table",
                                   paste0(file_name, ".png")), 
         width = 1, height = 0.2, type = "cairo", bg = "transparent", dpi = 300)

  output <- tibble(spark = md_img, summary = inline_summary)
  return(output)
}

my_summary <- function(x, variable, df) {
  x <- my_as_numeric(x)

  if (is.numeric(x)) {
    numeric_summary(x, variable)
  } else {
    level_summary(x, variable, df)
  }
}
```

@@

plot_dag %T>% 
  print() %T>%
  ggsave(., filename = here("output", "figures", "causal-path.pdf"),
         width = 4.5, height = 2.5, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = here("output", "figures", "causal-path.png"),
         width = 4.5, height = 2.5, units = "in", type = "cairo", dpi = 300)
```

@@

```{r check-conditions, results="asis"}
results %>% count(crackdown, issue, funding) %>% 
  rename(Crackdown = crackdown, Issue = issue, Funding = funding) %>% 
  janitor::adorn_totals(., where = "row") %T>% 
  pandoc.table() %>% 
  pandoc.table.return(caption = "Balance of experimental conditions {#tbl:experimental-conditions}") %>% 
  cat(file = here("output", "tables", "tbl-experimental-conditions.md"))
```

@@

results_summary_stats <- results %>% 
  select(one_of(vars_to_summarize$variable)) %>% 
  gather(variable, value) %>% 
  group_by(variable) %>% 
  nest() %>% 
  mutate(N = data %>% map_int(~ nrow(.)),
         summary = map2(.x = data, .y = variable, ~ my_summary(.x$value, .y, results))) %>% 
  left_join(vars_to_summarize, by = "variable") %>% 
  mutate(variable = factor(variable, levels = vars_to_summarize$variable, ordered = TRUE)) %>% 
  arrange(variable) %>% 
  select(-data, -variable) %>% 
  unnest(summary) %>% 
  select(Variable = clean_name, N, ` ` = spark, Details = summary)

results_summary_stats %>% 
  select(-N) %>% 
  pandoc.table.return(caption = "Descriptive statistics {#tbl:descriptive-stats}",
                      split.cell = 80, split.table = Inf) %T>% 
  cat(file = here("output", "tables", "tbl-descriptive-stats.md")) %>%
  cat()
```

@@

conditions_summary_clean %T>% 
  pandoc.table() %>% 
  pandoc.table.return(caption = "Average likelihood and amount donated across experimental conditions {#tbl:avg-results}") %>% 
  cat(file = here("output", "tables", "tbl-avg-results.md"))
```

@@

plot_donate_summary %T>% 
  print() %T>%
  ggsave(., filename = here("output", "figures", "donate_summary.pdf"),
         width = 9, height = 4, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = here("output", "figures", "donate_summary.png"),
         width = 9, height = 4, units = "in", type = "cairo", dpi = 300)
```

@@

plot_amount_summary %T>% 
  print() %T>%
  ggsave(., filename = here("output", "figures", "amount_summary.pdf"),
         width = 9, height = 2.75, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = here("output", "figures", "amount_summary.png"),
         width = 9, height = 2.75, units = "in", type = "cairo", dpi = 300)
```

@@

likely_theta %T>% 
  ggsave(., filename = here("output", "figures", "prior-likely.pdf"),
         width = 2.75, height = 1.5, units = "in", device = cairo_pdf) %>%
  ggsave(., filename = here("output", "figures", "prior-likely.png"),
         width = 2.75, height = 1.5, units = "in", type = "cairo", dpi = 300)
```

@@

```{r run-likely-models, results="hide", cache=TRUE}
# This takes forever because of C++ compiling and actual MCMC sampling, so this
# chunk is cached

# Compile model
donate_likely <- stan_model(here("lib", "donate_likely.stan"))

@@

    return(list(
      n_total_1 = df_counts$total[1],
      n_total_2 = df_counts$total[2],
      n_likely_1 = df_counts$n[1],
      n_likely_2 = df_counts$n[2]
    ))
  })) %>% 
  # Run the actual model on the simplified data
  mutate(model = stan_data_counts %>% map(~ {
    sampling(donate_likely, data = .x, control = list(max_treedepth = 15),
             chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
  }))

@@

plot_diffs_likely_all %T>% 
  ggsave(., filename = here("output", "figures", "likely-diffs.pdf"),
         width = 4.5, height = 6.5, units = "in", device = cairo_pdf) %>%
  ggsave(., filename = here("output", "figures", "likely-diffs.png"),
         width = 4.5, height = 6.5, units = "in", type = "cairo", dpi = 300)
```

@@

bind_rows(tbl_likely_1, 
          tbl_likely_2_header, 
          set_names(tbl_likely_2, colnames(tbl_likely_1)),
          tbl_likely_3_header,
          set_names(tbl_likely_3, colnames(tbl_likely_1))) %>% 
  rename(`H~1a~` = Frame) %>% 
  pandoc.table.return(caption = 'Likelihood of donation and differences in proportions in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:likely-diffs}',
                      justify = "lccccc") %T>%
  cat() %>%
  cat(file = here("output", "tables", "tbl-likely-diffs.md"))
```

@@

amount_priors %T>% 
  ggsave(., filename = here("output", "figures", "prior-amount.pdf"),
         width = 8, height = 1.5, units = "in", device = cairo_pdf) %>%
  ggsave(., filename = here("output", "figures", "prior-amount.png"),
         width = 8, height = 1.5, units = "in", type = "cairo", dpi = 300)
```

@@

```{r run-amount-models, results="hide", cache=TRUE}
# This takes forever because of C++ compiling and actual MCMC sampling, so this
# chunk is cached

# Compile model
amount_donated_best <- stan_model(here("lib", "amount_donated_best.stan"))

# Sample from the compiled model
all_models_amount_run <- all_models %>% 
  # Simplify data for sending to Stan
  mutate(stan_data = df %>% map(~ {
    select(.x, amount = amount_donate, group = crackdown)
  })) %>% 
  # Run the actual model on the simplified data
  mutate(model = stan_data %>% map(~ {
    sampling(amount_donated_best, data = compose_data(.x),
             chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
  }))

@@

plot_diffs_amounts_all %T>% 
  ggsave(., filename = here("output", "figures", "amount-diffs.pdf"),
         width = 4.5, height = 6.5, units = "in", device = cairo_pdf) %>%
  ggsave(., filename = here("output", "figures", "amount-diffs.png"),
         width = 4.5, height = 6.5, units = "in", type = "cairo", dpi = 300)
```

@@

bind_rows(tbl_amount_1, 
          tbl_amount_2_header, 
          set_names(tbl_amount_2, colnames(tbl_amount_1)),
          tbl_amount_3_header,
          set_names(tbl_amount_3, colnames(tbl_amount_1))) %>% 
  rename(`H~1b~` = Frame) %>% 
  pandoc.table.return(caption = 'Mean values and differences in means for amount donated in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:amount-diffs}',
                      justify = "lccccc") %T>%
  cat() %>%
  cat(file = here("output", "tables", "tbl-amount-diffs.md"))
```

>>>>

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(crackdownsphilanthropy)
library(rstan)
library(tidybayes)
library(broom)
library(ggstance)
library(ggdag)
library(patchwork)
library(pander)
library(scales)
library(janitor)
library(here)

source(here("analysis", "options.R"))

# Load data
results <- readRDS(here("data", "derived_data", "results_clean.rds"))
# qwraps2::lazyload_cache_dir("02_analysis_cache/html")
```

@@

plot_dag %T>% 
  print() %T>%
  ggsave(., filename = here("analysis", "output", "figures", "causal-path.pdf"),
         width = 4.5, height = 2.5, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = here("analysis", "output", "figures", "causal-path.png"),
         width = 4.5, height = 2.5, units = "in", type = "cairo", dpi = 300)
```

@@

```{r check-conditions, results="asis"}
results %>% count(crackdown, issue, funding) %>% 
  rename(Crackdown = crackdown, Issue = issue, Funding = funding) %>% 
  janitor::adorn_totals(., where = "row") %T>% 
  pandoc.table() %>% 
  pandoc.table.return(caption = "Balance of experimental conditions {#tbl:experimental-conditions}") %>% 
  cat(file = here("analysis", "output", "tables", "tbl-experimental-conditions.md"))
```

@@

results_summary_stats <- results %>% 
  select(one_of(vars_to_summarize$variable)) %>% 
  gather(variable, value) %>% 
  group_by(variable) %>% 
  nest() %>% 
  mutate(N = data %>% map_int(~ nrow(.)),
         summary = map2(.x = data, .y = variable, ~ md_summary_row(.x$value, .y, results))) %>% 
  left_join(vars_to_summarize, by = "variable") %>% 
  mutate(variable = factor(variable, levels = vars_to_summarize$variable, ordered = TRUE)) %>% 
  arrange(variable) %>% 
  select(-data, -variable) %>% 
  unnest(summary) %>% 
  select(Variable = clean_name, N, ` ` = spark, Details = summary)

results_summary_stats %>% 
  select(-N) %>% 
  pandoc.table.return(caption = "Descriptive statistics {#tbl:descriptive-stats}",
                      split.cell = 80, split.table = Inf) %T>% 
  cat(file = here("analysis", "output", "tables", "tbl-descriptive-stats.md")) %>%
  cat()
```

@@

conditions_summary_clean %T>% 
  pandoc.table() %>% 
  pandoc.table.return(caption = "Average likelihood and amount donated across experimental conditions {#tbl:avg-results}") %>% 
  cat(file = here("analysis", "output", "tables", "tbl-avg-results.md"))
```

@@

plot_donate_summary %T>% 
  print() %T>%
  ggsave(., filename = here("analysis", "output", "figures", "donate_summary.pdf"),
         width = 9, height = 4, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = here("analysis", "output", "figures", "donate_summary.png"),
         width = 9, height = 4, units = "in", type = "cairo", dpi = 300)
```

@@

plot_amount_summary %T>% 
  print() %T>%
  ggsave(., filename = here("analysis", "output", "figures", "amount_summary.pdf"),
         width = 9, height = 2.75, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = here("analysis", "output", "figures", "amount_summary.png"),
         width = 9, height = 2.75, units = "in", type = "cairo", dpi = 300)
```

@@

likely_theta %T>% 
  ggsave(., filename = here("analysis", "output", "figures", "prior-likely.pdf"),
         width = 2.75, height = 1.5, units = "in", device = cairo_pdf) %>%
  ggsave(., filename = here("analysis", "output", "figures", "prior-likely.png"),
         width = 2.75, height = 1.5, units = "in", type = "cairo", dpi = 300)
```

@@

```{r run-likely-models, results="hide", cache=TRUE}
# This takes forever because of MCMC sampling, so this chunk is cached

@@

    return(list(
      n_total_1 = df_counts$total[1],
      n_total_2 = df_counts$total[2],
      n_likely_1 = df_counts$n[1],
      n_likely_2 = df_counts$n[2]
    ))
  })) %>% 
  # Run the actual model on the simplified data
  mutate(model = stan_data_counts %>% map(~ {
    sampling(donate_likely(), data = .x, control = list(max_treedepth = 15),
             chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
  }))

@@

plot_diffs_likely_all %T>% 
  ggsave(., filename = here("analysis", "output", "figures", "likely-diffs.pdf"),
         width = 4.5, height = 6.5, units = "in", device = cairo_pdf) %>%
  ggsave(., filename = here("analysis", "output", "figures", "likely-diffs.png"),
         width = 4.5, height = 6.5, units = "in", type = "cairo", dpi = 300)
```

@@

bind_rows(tbl_likely_1, 
          tbl_likely_2_header, 
          set_names(tbl_likely_2, colnames(tbl_likely_1)),
          tbl_likely_3_header,
          set_names(tbl_likely_3, colnames(tbl_likely_1))) %>% 
  rename(`H~1a~` = Frame) %>% 
  pandoc.table.return(caption = 'Likelihood of donation and differences in proportions in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:likely-diffs}',
                      justify = "lccccc") %T>%
  cat() %>%
  cat(file = here("analysis", "output", "tables", "tbl-likely-diffs.md"))
```

@@

amount_priors %T>% 
  ggsave(., filename = here("analysis", "output", "figures", "prior-amount.pdf"),
         width = 8, height = 1.5, units = "in", device = cairo_pdf) %>%
  ggsave(., filename = here("analysis", "output", "figures", "prior-amount.png"),
         width = 8, height = 1.5, units = "in", type = "cairo", dpi = 300)
```

@@

```{r run-amount-models, results="hide", cache=TRUE}
# Sample from the compiled model
all_models_amount_run <- all_models %>% 
  # Simplify data for sending to Stan
  mutate(stan_data = df %>% map(~ {
    select(.x, amount = amount_donate, group = crackdown)
  })) %>% 
  # Run the actual model on the simplified data
  mutate(model = stan_data %>% map(~ {
    sampling(amount_donated_best(), data = compose_data(.x),
             chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
  }))

@@

plot_diffs_amounts_all %T>% 
  ggsave(., filename = here("analysis", "output", "figures", "amount-diffs.pdf"),
         width = 4.5, height = 6.5, units = "in", device = cairo_pdf) %>%
  ggsave(., filename = here("analysis", "output", "figures", "amount-diffs.png"),
         width = 4.5, height = 6.5, units = "in", type = "cairo", dpi = 300)
```

@@

bind_rows(tbl_amount_1, 
          tbl_amount_2_header, 
          set_names(tbl_amount_2, colnames(tbl_amount_1)),
          tbl_amount_3_header,
          set_names(tbl_amount_3, colnames(tbl_amount_1))) %>% 
  rename(`H~1b~` = Frame) %>% 
  pandoc.table.return(caption = 'Mean values and differences in means for amount donated in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:amount-diffs}',
                      justify = "lccccc") %T>%
  cat() %>%
  cat(file = here("analysis", "output", "tables", "tbl-amount-diffs.md"))
```

### 2019-03-08 analysis/03_additional-analysis.Rmd
HUGE reorganization (go to 0290370 for previous history)
Switched this to build as a package using rrtools, with pre-built Stan binaries through rstantools. As a result, everything got shuffled around, and GitHub doesn't use --follow in their logs, so the history is hidden. Going to 02903709c87b79e8a945dd31fafd2484cbf2bc7b and going back in history from there will let you see past changes to these files.

In general, here's what happened:

- All analysis files in the project root (Rmd files that generated the website) are now in /analysis/*
- R functions that lived in lib/* are now standalone

```{r load-libraries-data, warning=FALSE, message=FALSE}
# Load libraries
library(tidyverse)
library(magrittr)
library(rstan)
library(rstanarm)
library(broom)
library(glue)
library(ggstance)
library(ggridges)
library(grid)
library(gridExtra)
library(Gmisc)
library(patchwork)
library(pander)
library(scales)
library(huxtable)
library(lubridate)
library(modelr)
library(ipumsr)
library(here)

source(here("lib", "graphics.R"))
source(here("lib", "pander_options.R"))
source(here("lib", "modeling.R"))

# Load data
results <- readRDS(here("data", "results_clean.rds"))
```

@@

```{r build-consort}
consort <- readRDS(here("data", "completion_summary.rds")) %>% 
  spread(reason, n) %>% 
  mutate(group = 1:n(),
         assigned = Approved + `Failed first attention check`,
         issue = str_replace_all(issue, "assistance", "assist.")) %>% 
  mutate(assigned_label = glue("Allocated to Group {group}\n{crackdown}\n{issue}\n{funding} funding\n\nN = {assigned}"),
         completed_label = glue("Completed\nN = {Approved}\n\n{`Failed first attention check`} failed\nattention check"))

@@

# Save as PDF
cairo_pdf(filename = here("output", "figures", "consort.pdf"),
          width = 10, height = 6)
grid.newpage()
walk(full_chart, ~ print(.))
invisible(dev.off())

# Save as PNG
png(filename = here("output", "figures", "consort.png"), 
    width = 10, height = 6, units = "in",
    bg = "white", res = 300, type = "cairo")
grid.newpage()
walk(full_chart, ~ print(.))
invisible(dev.off())

@@

```{r load-clean-cps, warning=FALSE, message=FALSE}
cps_2015_ddi_file <- here("data", "ipums-cps", "cps_09_2015.xml")
cps_2015_data_file <- here("data", "ipums-cps", "cps_09_2015.dat.gz")

@@

cps_2017_ddi_file <- here("data", "ipums-cps", "cps_2017.xml")
cps_2017_data_file <- here("data", "ipums-cps", "cps_2017.dat.gz")

@@

```{r sample-population-characteristics-freq, include=FALSE, eval=FALSE}
# Demographic variables
table(results$gender_bin) %>% prop.test(., p = global_stats$female)
table(results$education_bin) %>% prop.test(., p = global_stats$college)
table(results$income_bin) %>% prop.test(., p = global_stats$income)
table(results$age_bin) %>% prop.test(., p = global_stats$age)

# Volunteering
table(results$volunteer) %>% prop.test(., p = global_stats$volunteering)
table(results$give_charity_2) %>% prop.test(., p = global_stats$donating)
```

```{r compile-stan-model, warning=FALSE, message=FALSE, cache=TRUE}
prop_test_bayes_saved <- here("lib", "bayes_prop_test.rds")

if (file.exists(prop_test_bayes_saved)) {
  prop_test_bayes <- readRDS(prop_test_bayes_saved)
} else {
  prop_test_bayes <- stan_model(here("lib", "bayes_prop_test.stan"))
  saveRDS(prop_test_bayes, prop_test_bayes_saved)
}
```

```{r sample-population-characteristics, cache=TRUE}
compare_sample_to_pop_bayes <- function(sample_value, population_value) {
  mcmc_samples <- sampling(prop_test_bayes, list(x = table(sample_value)[1],
                                                 total_n = length(sample_value),
                                                 pop_prop = population_value),
                           chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)

@@

calc_sample_pop <- tribble(
  ~Variable, ~sample_value, ~National,
  "Female (%)^a^", results$gender_bin, global_stats$female,
  "Age (% 35+)^a^", results$age_bin, global_stats$age,
  "Income (% $50,000+)^a^", results$income_bin, global_stats$income,
  "Education (% BA+)^a^", results$education_bin, global_stats$college,
  "Donated in past year (%)^b^", results$give_charity_2, global_stats$donating,
  "Volunteered in past year (%)^b^", results$volunteer, global_stats$volunteering
) %>% 
  mutate(Sample = sample_value %>% map_dbl(~ prop.table(table(.))[1]),
         prop_test_bayes = map2(.x = sample_value, .y = National, 
                                .f = ~ compare_sample_to_pop_bayes(.x, .y))) 
```

@@

bind_rows(tbl_sample_pop, note_row) %>% 
  pandoc.table.return(keep.line.breaks = TRUE, style = "multiline", justify = "lcccc", 
                      caption = "Characteristics of experimental sample {#tbl:exp-sample}") %T>% 
  cat(file = here("output", "tables", "tbl-exp-sample.md")) %>% 
  cat()
```

@@

```{r avg-time, results="asis"}
fmt_ms <- function(x) {
  n_seconds <- seconds_to_period(x)
  sprintf("%02.0f:%02.0f", minute(n_seconds), second(n_seconds))
}

theme_ngos_table <- ttheme_minimal(
  core = 
    list(fg_params = 
           list(hjust = 0, x = 0.1,
                fontsize = 7, fontface = "plain",
                fontfamily = "Roboto Condensed Light"),
         bg_params = list(fill = "white")),
  colhead = 
    list(fg_params = 
           list(hjust = 0, x = 0.1, col = "white",
                fontsize = 7, fontface = "plain",
                fontfamily = "Roboto Condensed Bold"),
         bg_params = list(fill = ngo_cols("blue"))),
  padding = unit(c(4, 2), "mm"))

time_summary <- results %>% 
  summarize_at(vars(duration), funs(Minimum = min, Maximum = max, Mean = mean, 
                                    `Standard deviation` = sd, Median = median)) %>% 
  gather(Statistic, value) %>% 
  mutate(Minutes = fmt_ms(value)) %>% 
  select(-value)

@@

plot_avg_time <- ggplot(results, aes(x = duration)) +
  geom_histogram(bins = 50, fill = ngo_cols("blue")) +
  scale_x_time(labels = fmt_ms) +
  annotation_custom(summary_stats, xmin = 700, xmax = 900, ymin = 30, ymax = 60) +
  labs(x = "Minutes spent on experiment", y = "Count") +
  theme_ngos(base_size = 9.5) +
  theme(panel.grid.minor = element_blank())

plot_avg_time %T>% 
  print() %T>%
  ggsave(., filename = here("output", "figures", "avg-time.pdf"),
         width = 4, height = 2.25, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = here("output", "figures", "avg-time.png"),
         width = 4, height = 2.25, units = "in", type = "cairo", dpi = 300)
```

>>>>

```{r load-libraries-data, warning=FALSE, message=FALSE}
# Load libraries
library(tidyverse)
library(crackdownsphilanthropy)
library(magrittr)
library(rstan)
library(broom)
library(glue)
library(grid)
library(gridExtra)
library(Gmisc)
library(pander)
library(scales)
library(ipumsr)
library(here)

source(here("analysis", "options.R"))

# Load data
results <- readRDS(here("data", "derived_data", "results_clean.rds"))
```

@@

```{r build-consort}
consort <- readRDS(here("data", "derived_data", "completion_summary.rds")) %>% 
  spread(reason, n) %>% 
  mutate(group = 1:n(),
         assigned = Approved + `Failed first attention check`,
         issue = str_replace_all(issue, "assistance", "assist.")) %>% 
  mutate(assigned_label = glue("Allocated to Group {group}\n{crackdown}\n{issue}\n{funding} funding\n\nN = {assigned}"),
         completed_label = glue("Completed\nN = {Approved}\n\n{`Failed first attention check`} failed\nattention check"))

@@

# Save as PDF
cairo_pdf(filename = here("analysis", "output", "figures", "consort.pdf"),
          width = 10, height = 6)
grid.newpage()
walk(full_chart, ~ print(.))
invisible(dev.off())

# Save as PNG
png(filename = here("analysis", "output", "figures", "consort.png"), 
    width = 10, height = 6, units = "in",
    bg = "white", res = 300, type = "cairo")
grid.newpage()
walk(full_chart, ~ print(.))
invisible(dev.off())

@@

```{r load-clean-cps, warning=FALSE, message=FALSE}
cps_2015_ddi_file <- here("data", "raw_data", "ipums-cps", "cps_09_2015.xml")
cps_2015_data_file <- here("data", "raw_data", "ipums-cps", "cps_09_2015.dat.gz")

@@

cps_2017_ddi_file <- here("data", "raw_data", "ipums-cps", "cps_2017.xml")
cps_2017_data_file <- here("data", "raw_data", "ipums-cps", "cps_2017.dat.gz")

@@

```{r sample-population-characteristics, cache=TRUE}
compare_sample_to_pop <- function(sample_value, population_value) {
  mcmc_samples <- pop_prop_stan(
    x = table(sample_value)[1],
    n_total = length(sample_value),
    pop_prop = population_value,
    chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)

@@

calc_sample_pop <- tribble(
  ~Variable, ~sample_value, ~National,
  "Female (%)^a^", results$gender_bin, global_stats$female,
  "Age (% 35+)^a^", results$age_bin, global_stats$age,
  "Income (% $50,000+)^a^", results$income_bin, global_stats$income,
  "Education (% BA+)^a^", results$education_bin, global_stats$college,
  "Donated in past year (%)^b^", results$give_charity_2, global_stats$donating,
  "Volunteered in past year (%)^b^", results$volunteer, global_stats$volunteering
) %>% 
  mutate(Sample = sample_value %>% map_dbl(~ prop.table(table(.))[1]),
         prop_test_bayes = map2(.x = sample_value, .y = National, 
                                .f = ~ compare_sample_to_pop(.x, .y))) 
```

@@

bind_rows(tbl_sample_pop, note_row) %>% 
  pandoc.table.return(keep.line.breaks = TRUE, style = "multiline", justify = "lcccc", 
                      caption = "Characteristics of experimental sample {#tbl:exp-sample}") %T>% 
  cat(file = here("analysis", "output", "tables", "tbl-exp-sample.md")) %>% 
  cat()
```

@@

```{r avg-time, results="asis"}
time_summary <- results %>% 
  summarize_at(vars(duration), funs(Minimum = min, Maximum = max, Mean = mean, 
                                    `Standard deviation` = sd, Median = median)) %>% 
  gather(Statistic, value) %>% 
  mutate(Minutes = fmt_seconds(value)) %>% 
  select(-value)

@@

plot_avg_time <- ggplot(results, aes(x = duration)) +
  geom_histogram(bins = 50, fill = ngo_cols("blue")) +
  scale_x_time(labels = fmt_seconds) +
  annotation_custom(summary_stats, xmin = 700, xmax = 900, ymin = 30, ymax = 60) +
  labs(x = "Minutes spent on experiment", y = "Count") +
  theme_ngos(base_size = 9.5) +
  theme(panel.grid.minor = element_blank())

plot_avg_time %T>% 
  print() %T>%
  ggsave(., filename = here("analysis", "output", "figures", "avg-time.pdf"),
         width = 4, height = 2.25, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = here("analysis", "output", "figures", "avg-time.png"),
         width = 4, height = 2.25, units = "in", type = "cairo", dpi = 300)
```

### 2019-03-08 analysis/index.Rmd
HUGE reorganization (go to 0290370 for previous history)
Switched this to build as a package using rrtools, with pre-built Stan binaries through rstantools. As a result, everything got shuffled around, and GitHub doesn't use --follow in their logs, so the history is hidden. Going to 02903709c87b79e8a945dd31fafd2484cbf2bc7b and going back in history from there will let you see past changes to these files.

In general, here's what happened:

- All analysis files in the project root (Rmd files that generated the website) are now in /analysis/*
- R functions that lived in lib/* are now standalone

---
title: "NGO Crackdowns and Philanthropy"
author: "Suparna Chaudhry and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
site: safesite::safesite
---

>>>>

---
title: "NGO Crackdowns and Philanthropy"
author: "Suparna Chaudhry and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
---
